DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems with PDEs

### 2012-12-10 Paper_May_2012/Anschreiben/LetterToTheEditior_ACMTOMS.tex

\begin{document}
\thiswatermark{\begin{minipage}{\textwidth}\vspace*{43.5cm}\hspace*{5.8cm}\includegraphics[width=0.8\textwidth]{BG_logo}
  \end{minipage}
}
\begin{letter}{Editor-in-Chief of Computing\\Prof. Dr. Schahram Dustdar\\[\baselineskip]
    electronic}

@@

\opening{Dear Professor Dustdar,}

@@

for publication in Computing by
C.Goll, T. Wick and W. Wollner.

The article outlines the guiding design principles of our software environment
DOpElib (see \url{dopelib.net}) for the numerical solution of PDEs and optimization problems subject 
to PDEs with special emphasis on modular design of all components. 
We hope that you deem this publication worthy of publication in Computing.

>>>>

\begin{document}
\thiswatermark{\begin{minipage}{\textwidth}\vspace*{43.5cm}\hspace*{5.8cm}\includegraphics[width=0.8\textwidth]{BG_logo}
  \end{minipage}
}
\begin{letter}{Editor-in-Chief of ACM Transactions on Mathematical Software\\Prof. Dr. Mike Heroux\\[\baselineskip]
    electronic}

@@

\opening{Dear Professor Heroux,}

@@

for publication in ACM Transactions on Mathematical Software by
C.Goll, T. Wick and W. Wollner.

The article outlines the guiding design principles of our software environment
DOpElib (see \url{dopelib.net}) for the numerical solution of PDEs and optimization problems subject 
to PDEs with special emphasis on modular design of all components. 
We hope that you deem this publication worthy of publication in ACM Transactions on Mathematical Software.
